A meta-analysis of mental rotation ability in the first years of life

### 2022-04-28 code/analysis.Rmd
Fix regression plot

    # Add unique experiment identifier
    experiment = str_c(year, article, group, seq = ", "),

@@

# Regression plot
dat_reg %>%
  ggplot(aes(x = age * 12, y = gi)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  # Regression lines and HPDIs - Habituation tasks
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - Habituation tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = habi_colors,
    breaks = names(habi_colors),
    labels = c("Females", "Males", "Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(
    title = "Habituation tasks",
    override.aes = list(fill = NA),
    order = 1
  )) +
  # Regression lines and HPDIs - VoE tasks
  ggnewscale::new_scale_color() +
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    fill = NA,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - VoE tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = voe_colors,
    breaks = names(voe_colors),
    labels = c("Mixed gender"),
    na.value = NA
  ) +
  guides(
    color = guide_legend(
      title = "Violation of\nexpectation tasks"
    ),
    order = 2
  ) +
  # Styling
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(limits = c(2.9, 16.1), breaks = seq(3, 16, 1)) +
  scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
  scale_fill_grey(
    start = 0.9, end = 0.7,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  labs(
    x = "Age (months)",
    y = expression("Hedges'" ~ italic("g")),
    fill = "Bayesian HPDI",
    size = "Sample size"
  ) +
  theme_bw() +
  theme(
    legend.direction = "vertical",
    legend.key = element_blank(),
    legend.position = "none",
    panel.border = element_rect(size = 1),
    panel.grid = element_blank(), # element_line(color = "grey90"),
    text = element_text(family = "Helvetica"),
  ) -> plot_reg

@@

# Plot posterior distributions of the regression coefficients
draws_reg_coef <- tidy_draws(res_brm_reg)
draws_reg_coef %>%
  select(coef_colnames) %>%
  gather() %>%
  mutate(coef = factor(key, levels = names(coef_colnames))) %>%
  ggplot(aes(x = value, y = fct_rev(coef))) +
  geom_vline(xintercept = 0) +
  stat_halfeye(point_interval = mean_hdi) +
  coord_cartesian(xlim = c(-1.25, 1.25)) +
  scale_x_continuous(breaks = seq(-1, 1, 0.5)) +
  labs(
    x = expression("Regression weight (" * Delta * italic("g") * ")"),
    y = NULL
  ) +
  theme_bw() +
  theme(
    panel.grid = element_blank(),
    axis.text.y = element_text(hjust = 1),
    panel.border = element_rect(size = 1)
  ) -> plot_coef

>>>>

    # Add unique experiment identifier
    experiment = str_c(year, article, group, sep = ", "),

@@

# Regression plot
dat_reg %>%
  ggplot(aes(x = age * 12, y = gi)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  # Regression lines and HPDIs - Habituation tasks
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - Habituation tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = habi_colors,
    breaks = names(habi_colors),
    labels = c("Females", "Males", "Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(
    title = "Habituation tasks",
    override.aes = list(fill = NA),
    order = 1
  )) +
  # Regression lines and HPDIs - VoE tasks
  ggnewscale::new_scale_color() +
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = draws_reg,
    alpha = .4,
    fill = NA,
    point_interval = "mean_hdi"
  ) +
  # Individual study effect sizes - VoE tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = voe_colors,
    breaks = names(voe_colors),
    labels = c("Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(title = "VoE tasks", order = 2)) +
  # Styling
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(limits = c(2.9, 16.1), breaks = seq(3, 16, 1)) +
  scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
  scale_fill_grey(
    start = 0.9, end = 0.7,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  labs(
    x = "Age (months)",
    y = expression("Hedges'" ~ italic("g")),
    fill = "Bayesian HPDI",
    size = "Sample size"
  ) +
  theme_bw() +
  theme(
    legend.direction = "vertical",
    legend.key = element_blank(),
    legend.position = "none",
    panel.border = element_rect(size = 1),
    panel.grid = element_blank(), # element_line(color = "grey90"),
    text = element_text(family = "Helvetica"),
  ) -> plot_reg

@@

# Define new labels for the regression coefficients
coef_colnames <- c(
  "Intercept" = "b_Intercept",
  "Females - mixed" = "b_gender2M1",
  "Males - females" = "b_gender3M2",
  "Age (per year)" = "b_age_c",
  "Habituation - VoE" = "b_task2M1",
  "(Females - Mixed) × age" = "b_gender2M1:age_c",
  "(Males - Females) × age" = "b_gender3M2:age_c"
)

# Plot posterior distributions of the regression coefficients
draws_reg_coef <- tidy_draws(res_brm_reg)
draws_reg_coef %>%
  select(all_of(coef_colnames)) %>%
  gather() %>%
  mutate(coef = factor(key, levels = names(coef_colnames))) %>%
  ggplot(aes(x = value, y = fct_rev(coef))) +
  geom_vline(xintercept = 0) +
  stat_halfeye(point_interval = mean_hdi) +
  coord_cartesian(xlim = c(-1.25, 1.25)) +
  scale_x_continuous(breaks = seq(-1, 1, 0.5)) +
  labs(
    x = expression("Regression weight (" * Delta * italic("g") * ")"),
    y = "Fixed effect"
  ) +
  theme_bw() +
  theme(
    panel.grid = element_blank(),
    axis.text.y = element_text(hjust = 1),
    panel.border = element_rect(size = 1)
  ) -> plot_coef
